\documentclass[handout, t]{beamer}
\usepackage[latin1]{inputenc}
\usepackage{pgfpages}
\pgfpagesuselayout{2 on 1}[a4paper,border shrink=5mm]
\mode<handout>{\setbeamercolor{background canvas}{bg=black!5}}
\usecolortheme[named=BurntOrange]{}
\title[DIM3 Project Presentation]{CodeBuzz}
\author{Team Gocky}
\institute{University Of Glasgow}
\date{\today}
\begin{document}


\section{Aims}

\begin{frame}
\frametitle{CodeBuzz By Team Gocky}
Aims:
\begin{itemize}
\item Facilitate programming language learning by exposing beginners to
example programs written by industry experts and academics.
\item Aid reuse by providing a store of solutions to commonly recurring
problems.
\item Simple, usable, and clean user interface.
\end{itemize}
\end{frame}

\section{User Requirements}

\subsection{The Noob, The Experienced, and The Academic}

\begin{frame}
\frametitle{Barry The Noob}
Barry's programming ability is, at best,
amateur. He relies heavily on introductory texts and Internet forums
since his school does not provide learning materials for the language
of interest.
\end{frame}

\begin{frame}
\frametitle{Joe The Academic}
Joe is a University Professor teaching software engineering at
one of the top universities in his country. He wishes to contribute
code to a publicly accessible forum for his research area to entice
people to join his research project entitled
\textit{Software Elasticity in Safety-Critical Systems}.
\end{frame}

\subsection{User Needs Matrix}

\begin{frame}
\frametitle{User Needs Matrix}
Our User Needs Matrix will go here!
\end{frame}

\section{Client Interface}

\begin{frame}
\frametitle{Wireframes}
This is the wireframes for the application:
\begin{itemize}
\item Logged in user
\item Annonymous user
\item Jane reviewing a snippet.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Walkthrough}
\begin{enumerate}
\item Joe logs in using his user details.
\item Joe is present with the home screen.
\item Joe selects the C programming language from the language drop-down
menu.
\item Joe proceeds to write his C code into the main window.
\item Joe selects the `Data Structures' category from the category
drop-down menu.
\item Joe is finished creating his code snippet and clicks the `Submit'
button.
\item Joe logs out.
\end{enumerate}
\end{frame}

\end{document}
